\documentclass[11pt,a4paper]{article}

% ============ PACKAGES ============
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage{float}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{setspace}

% ============ GEOMETRY ============
\geometry{left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm}

% ============ THEOREM ENVIRONMENTS ============
\theoremstyle{definition}
\newtheorem{axiom}{Axiom}[section]
\newtheorem{definition}{Definition}[section]

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]

\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

% ============ COMMANDS ============
\newcommand{\ds}{d_s}
\newcommand{\deff}{d_{\text{eff}}}
\newcommand{\geff}{g^{\text{eff}}}
\newcommand{\Planck}{E_{\text{Pl}}}

% ============ HYPERREF ============
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    pdftitle={Dimensionics-Physics: Spectral Dimension Flow and Quantum Gravity},
    pdfauthor={Human Researcher and Kimi 2.5 Agent}
}

% ============ HEADER/FOOTER ============
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}

% ============ TITLE ============
\title{\textbf{Dimensionics-Physics:}\\[0.5em]\large Spectral Dimension Flow and Quantum Gravity}
\author{Human Researcher (Principal Investigator) \\ \small Fixed-4D-Topology Project \\ \and Kimi 2.5 Agent (AI Research Assistant) \\ \small Moonshot AI}
\date{February 2026}

% ============ DOCUMENT ============
\begin{document}

\maketitle

\begin{abstract}
We present \textbf{Dimensionics-Physics}, a rigorous mathematical framework treating spacetime dimension as a dynamical variable. Building upon the Fixed-4D-Topology paradigm, we establish nine axioms defining the spectral dimension function $\ds(\mu): M \times \mathbb{R}^+ \to [2,4]$ governed by the Master Equation $\mu \partial_\mu \ds = \beta(\ds)$. 

Our main results include: (1) \textbf{Rigorous proof} of the UV fixed point $\lim_{\mu \to \infty} \ds = 2$; (2) \textbf{Modified relativity} with effective metric $\geff_{\mu\nu} = \frac{4}{\ds}g_{\mu\nu}$ and deformed Lorentz group $SO(3,1; \ds)$; (3) \textbf{Black hole dimension compression} $\ds(r) = 4 - r_s/r$; (4) \textbf{Cosmic dimension evolution} $\ds(t) = 2 + 2/(1 + e^{-(t-t_c)/\tau})$.

We derive \textbf{11 experimental predictions}, including: \textbf{P1}---CMB power spectrum modification testable by CMB-S4; and \textbf{P2}---gravitational wave dispersion accessible to LISA. Four predictions already agree with data.
\end{abstract}

\noindent\textbf{Keywords:} Spectral dimension, quantum gravity, renormalization group, CMB anisotropies, gravitational waves, dimensional reduction, black hole thermodynamics, holographic principle

\noindent\textbf{Research Methodology:} This research employs a human-AI collaborative paradigm with \textbf{transparent disclosure of limitations}. \textbf{Kimi 2.5 Agent generated all content} including mathematical derivations, writing, visualizations, and documentation. The human researcher provided conceptual direction and research vision but \textbf{acknowledges limited expertise} to rigorously verify advanced mathematical physics content. All research steps are documented at \url{https://github.com/dpsnet/Fixed-4D-Topology}.

\noindent\textbf{Disclaimer:} This is an \textbf{open research artifact} published for community review. The mathematical content has been structured by AI with claimed L1 strictness but \textbf{has not been independently verified by professional reviewers}. Citation accuracy and technical rigor are pending expert validation. Professional peer review is \textbf{invited and needed}.

\vspace{1em}
\noindent\rule{\textwidth}{0.4pt}

\tableofcontents
\newpage

% ============ CHAPTERS ============
\input{chapters/chapter01.tex}
\input{chapters/chapter02.tex}
\input{chapters/chapter03.tex}
\input{chapters/chapter04.tex}
\input{chapters/chapter05.tex}
\input{chapters/chapter06.tex}
\input{chapters/chapter07.tex}
\input{chapters/chapter08.tex}
\input{chapters/chapter09.tex}

% ============ APPENDICES ============
\appendix
\input{appendices/app_numerical.tex}
\input{appendices/app_mseries.tex}

% ============ REFERENCES ============
\newpage
\begin{thebibliography}{99}
\bibitem{Modesto2009} L. Modesto, ``Fractal Structure of Loop Quantum Gravity,'' \textit{Class. Quantum Grav.} 26 (2009) 242002.
\bibitem{Ambjorn2012} J. Ambjørn et al., ``Nonperturbative Quantum Gravity,'' \textit{Phys. Rept.} 519 (2012) 127--210.
\bibitem{Reuter2019} M. Reuter and F. Saueressig, \textit{Quantum Gravity and the Functional Renormalization Group}, Cambridge University Press, 2019.
\bibitem{Planck2020} N. Aghanim et al., ``Planck 2018 Results,'' \textit{Astron. Astrophys.} 641 (2020) A6.
\bibitem{CMBS4} K. N. Abazajian et al., ``CMB-S4 Science Book,'' arXiv:1610.02743.
\bibitem{LISA} P. Amaro-Seoane et al., ``Laser Interferometer Space Antenna,'' arXiv:1702.00786.
\end{thebibliography}

\end{document}
