\documentclass[11pt,a4paper]{article}

% 基础包
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{tikz}

% 页面设置
\geometry{margin=2.5cm}

% 定理环境
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}

% 标题信息
\title{\textbf{Spectral Flow as Energy-Dependent Mode Constraint}\\[0.5em]
\large Historical Terminology Clarification and Unified Framework for Constrained Dynamics}

\author{
    Wang Bin$^1$ \quad Kimi 2.5 Agent$^2$ \\[0.5em]
    \small $^1$Independent Researcher, \href{mailto:wang.bin@foxmail.com}{wang.bin@foxmail.com} \\
    \small $^2$Personal Research
}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This comprehensive review presents a unified framework for understanding the phenomenon variously termed ``spectral dimension flow,'' ``running dimension,'' or ``dimensional reduction'' in the quantum gravity literature. We trace the historical evolution of terminology from Minakshisundaram and Pleijel's 1949 foundational work through modern applications, identifying sources of conceptual confusion and establishing a precise three-level framework distinguishing topological dimension, spectral dimension as a mathematical probe, and effective degrees of freedom as a physical quantity.

The phenomenon is most accurately described as \textbf{energy-dependent constraint on dynamical degrees of freedom}, where physical mechanisms (centrifugal forces, gravitational redshift, quantum geometric discreteness) create energy gaps that freeze certain modes, leaving only a subset accessible to low-energy probes. The universal scaling of constraint onset follows $c_1(d,w) = 1/2^{d_{\text{topo}}-2+w}$ across rotating systems, black holes, and quantum spacetime.

We develop the mathematical foundations through detailed heat kernel analysis, explore the physical mechanisms in three canonical systems, review extensive experimental and numerical evidence, and discuss implications for black hole physics, quantum gravity, and the emergence of effective field theories. Throughout, we maintain terminological precision: spacetime topology remains fixed while the \textbf{accessibility} of dynamical modes changes with energy scale.

\end{abstract}

\tableofcontents
\newpage

% ========== 符号表 ==========
\section*{Notation and Terminology Guide}
\addcontentsline{toc}{section}{Notation and Terminology Guide}

\begin{longtable}{@{}p{3.5cm}p{11.5cm}@{}}
\toprule
\textbf{Term} & \textbf{Precise Definition and Usage} \\
\midrule
\endhead
$d_{\text{topo}}$ & \textbf{Topological dimension}: Intrinsic dimension of spacetime manifold. Fixed at 4 for physical spacetime. Never changes with energy scale. \\
\addlinespace
d_s(\tau) & \textbf{Spectral dimension}: Mathematical parameter defined by $-2 d\ln K/d\ln\tau$. A \textit{measure} or \textit{probe} of mode accessibility, not a physical dimension. \\
\addlinespace
$n_{\text{dof}}(E)$ & \textbf{Effective degrees of freedom}: Number of dynamical directions accessible at energy $E$. Physical quantity approximated by $d_s(\tau)$ when $E \sim \hbar/\tau$. \\
\addlinespace
Mode constraint & Physical mechanism where energy gaps freeze dynamical modes, reducing $n_{\text{dof}}$ at low energy. \\
\addlinespace
Mode freezing & Decoupling of high-gap modes from low-energy physics due to energy constraints. Modes remain in principle but are exponentially suppressed. \\
\addlinespace
Spectral flow & Variation of $d_s(\tau)$ with scale $\tau$. Describes changing mode accessibility, not physical dimension change. \\
\addlinespace
$c_1(d,w)$ & Universal constraint parameter $= 1/2^{d_{\text{topo}}-2+w}$. Characterizes sharpness of constraint onset. $w=0$ (classical), $w=1$ (quantum). \\
\addlinespace
$K(\tau)$ & Heat kernel trace: measure of accessible mode density at diffusion time $\tau$. \\
\addlinespace
$E_{\text{gap}}$ & Energy gap required to excite a constrained mode. Modes with $E_{\text{gap}} \gg E$ are frozen at energy $E$. \\
\addlinespace
$\tau_c$ & Characteristic constraint scale. Determines energy scale at which constraint becomes significant. \\
\bottomrule
\end{longtable}

\vspace{1em}
\textbf{Important Clarifications}:
\begin{itemize}
\item We avoid ``dimension flow'' as ambiguous; use ``spectral flow'' (parameter change) or ``mode constraint'' (physical mechanism).
\item ``Dimensional reduction'' is reserved for genuine topological change (e.g., Kaluza-Klein compactification), not for mode constraint.
\item ``Effective dimension'' refers to $n_{\text{dof}}$, distinct from topological dimension.
\end{itemize}

\newpage

% ========== 使用扩展版章节 ==========
\input{chapters/chapter1_reconstructed}    % 重构版引言（含历史分析）
\input{chapters/chapter2_extended}         % 扩展版数学框架（713行）
\input{chapters/figures_all}               % 所有研究数据图表整合
\input{chapters/chapter2_related_frameworks} % 相关框架（136行）
\input{chapters/chapter3_extended}         % 扩展版三系统（500行）
\input{chapters/chapter4_extended}         % 扩展版实验（387行）
\input{chapters/chapter_E6_experiment}    % E-6实验详细章节
\input{chapters/chapter_comparison}        % 批判比较（161行）
\input{chapters/chapter5_extended}         % 扩展版理论意义
\input{chapters/chapter6_extended}         % 扩展版展望

% ========== 附录 ==========
\appendix
\input{appendices_final}

% ========== 致谢 ==========
\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

This research was conducted independently without external funding support. The authors thank the developers of SnapPy for making their software freely available, and to the experimental groups who have provided high-precision data. The first author (王斌) acknowledges personal dedication to foundational physics research. The second author (Kimi 2.5 Agent) was employed as an AI research assistant for literature analysis and technical writing.

\bibliographystyle{plain}
\bibliography{references/extended_bibliography}

\end{document}
