\documentclass[11pt,a4paper]{article}

% 基础包
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{mathrsfs}
\usepackage{bm}

% 页面设置
\geometry{margin=2.5cm}

% 定理环境
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

% 标题信息
\title{\textbf{Spectral Flow as Energy-Dependent Mode Constraint}\\[0.5em]
\large Historical Terminology Clarification and Unified Physical Framework}

\author{Unified Field Theory Research Group}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This review presents a comprehensive analysis of the phenomenon variously termed ``spectral dimension flow,'' ``running dimension,'' or ``dimensional reduction'' in the quantum gravity literature. We trace the historical evolution of terminology from Minakshisundaram and Pleijel's 1949 foundational work through modern applications, identifying sources of conceptual confusion and establishing a precise three-level framework: (1) topological dimension (fixed at 4), (2) spectral dimension (mathematical probe parameter), and (3) effective degrees of freedom (physically accessible modes).

We demonstrate that the phenomenon is most accurately described as \textbf{energy-dependent constraint on dynamical degrees of freedom}, where energy gaps (from centrifugal forces, gravitational redshift, or quantum geometric discreteness) freeze certain modes, leaving only a subset accessible to low-energy probes. The universal scaling of constraint onset, characterized by $c_1(d,w) = 1/2^{d-2+w}$, emerges across rotating systems, black holes, and quantum spacetime.

Throughout, we emphasize terminological precision: spacetime does not ``become'' lower-dimensional; rather, the \textbf{accessibility} of dynamical modes changes with energy scale, while topological dimension remains fixed at 4.

\end{abstract}

\tableofcontents
\newpage

% 符号表
\section*{Notation and Terminology Guide}
\addcontentsline{toc}{section}{Notation and Terminology Guide}

\begin{longtable}{@{}p{3.5cm}p{11.5cm}@{}}
\toprule
\textbf{Term} & \textbf{Precise Definition and Usage} \\
\midrule
\endhead
$d_{\text{topo}}$ & \textbf{Topological dimension}: Intrinsic dimension of spacetime manifold. Fixed at 4 for physical spacetime. Never changes. \\
\addlinespace
$d_s(\tau)$ & \textbf{Spectral dimension}: Mathematical parameter defined by $-2 d\ln K/d\ln\tau$. A \textit{measure} of mode scaling, not a physical dimension. \\
\addlinespace
$n_{\text{dof}}(E)$ & \textbf{Effective degrees of freedom}: Number of dynamical directions accessible at energy $E$. Physical quantity approximated by $d_s(\tau)$. \\
\addlinespace
Mode constraint & Physical mechanism where energy gaps freeze certain dynamical modes, reducing effective degrees of freedom. \\
\addlinespace
Mode freezing & The decoupling of high-gap modes from low-energy physics due to energy constraints. \\
\addlinespace
Spectral flow & Variation of $d_s(\tau)$ with scale; describes changing mode accessibility, not physical dimension change. \\
\addlinespace
$c_1(d,w)$ & Universal constraint parameter $= 1/2^{d_{\text{topo}}-2+w}$. Characterizes sharpness of constraint onset. \\
\addlinespace
$w$ & Constraint type index: 0 (classical, sharp), 1 (quantum, gradual). \\
\addlinespace
$K(\tau)$ & Heat kernel trace. Measures density of accessible modes at diffusion time $\tau$. \\
\addlinespace
$E_{\text{gap}}$ & Energy gap required to excite a constrained mode. \\
\bottomrule
\end{longtable}

\vspace{1em}
\textbf{Terminological Clarifications}:
\begin{itemize}
\item We avoid ``dimension flow'' as ambiguous; use ``spectral flow'' (parameter change) or ``mode constraint'' (physical mechanism).
\item We avoid ``dimensional reduction'' for mode constraint; reserve for genuine topological change (e.g., Kaluza-Klein compactification).
\item ``Effective dimension'' refers to $n_{\text{dof}}$, not to be confused with $d_{\text{topo}}$.
\end{itemize}

\newpage

% 主章节
\input{chapters/chapter1_final}
\input{chapters/chapter2_final}
\input{chapters/chapter3_final}
\input{chapters/chapter4_final}
\input{chapters/chapter5_final}
\input{chapters/chapter6_final}

% 附录
\input{appendices_final}

% 致谢
\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}

We thank colleagues for discussions on terminology and physics, and the developers of SnapPy for their software.

\bibliographystyle{plain}
\bibliography{references/extended_bibliography}

\end{document}
