\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{geometry}
\usepackage{CJKutf8}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{booktabs}

\geometry{margin=1.5cm, top=2cm, bottom=2cm}

\definecolor{cnblue}{RGB}{0,0,139}
\definecolor{engray}{RGB}{60,60,60}

\newcommand{\CN}[1]{\textcolor{cnblue}{\textbf{[中]} #1}}
\newcommand{\EN}[1]{\textcolor{engray}{\textbf{[En]} #1}}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\small \CN{统一维度流理论} / \EN{Unified Dimension Flow Theory}}
\fancyfoot[C]{\thepage}

\title{\vspace{-0.5cm}\begin{CJK}{UTF8}{gbsn}\textbf{统一维度流理论综述}\\Unified Dimension Flow Theory\end{CJK}\\[0.3em]
\large \CN{完整逐句对照版} / \EN{Complete Sentence-by-Sentence Translation}}
\author{\begin{CJK}{UTF8}{gbsn}王斌\end{CJK} (Wang Bin)}
\date{February 2026}

\begin{document}
\begin{CJK}{UTF8}{gbsn}

\maketitle

\vspace{-0.3cm}
\begin{center}
\fbox{\parbox{0.9\textwidth}{
\centering
\textbf{\CN{本文档基于真实论文章节文件的完整逐句对照翻译。}}\\
\textbf{\EN{This document provides complete sentence-by-sentence translation based on actual paper chapters.}}\\
\CN{包含所有详细解释、公式和推导。} / \EN{Includes all detailed explanations, formulas, and derivations.}
}}
\end{center}
\vspace{0.3cm}

% 目录
\tableofcontents
\newpage

% 摘要
\section*{\CN{摘要} / \EN{Abstract}}
\addcontentsline{toc}{section}{摘要 / Abstract}

\CN{本文综述了维度流理论的最新进展，建立了一个统一框架，将量子引力、黑洞物理和凝聚态系统联系起来。谱维度 $d_s(\tau)$ 作为一个普适量，在高能（紫外）区域从 $d_{UV}=2$ 过渡到低能（红外）区域的 $d_{IR}=4$。我们推导了普适公式 $c_1(d,w)=1/2^{d-2+w}$，并通过三种独立方法验证：数值拓扑（SnapPy）、实验凝聚态物理（Cu$_2$O里德堡激子）和量子模拟（二维氢原子）。}

\EN{We present a comprehensive review of dimension flow theory, establishing a unified framework that connects quantum gravity, black hole physics, and condensed matter systems. The spectral dimension $d_s(\tau)$ emerges as a universal observable that transitions from $d_{UV} = 2$ at high energies to $d_{IR} = 4$ at low energies. We derive the universal formula $c_1(d,w) = 1/2^{d-2+w}$ and validate it through three independent approaches: numerical topology (SnapPy), experimental condensed matter (Cu$_2$O Rydberg excitons), and quantum simulations (2D hydrogen).}

\newpage

% 引入各章
\input{chapters/chapter1_full_bilingual}
\input{chapters/chapter2_full_bilingual}
\input{chapters/chapter3_full_bilingual}
\input{chapters/chapter4_full_bilingual}
\input{chapters/chapter5_full_bilingual}
\input{chapters/chapter6_full_bilingual}

\end{CJK}
\end{document}
