\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper, margin=1.5in}

\begin{document}

\begin{center}
\Large\textbf{Conflict of Interest Statement}
\end{center}

\vspace{2em}

We, the authors of ``Fractal Spectral Asymptotics and p-adic Thermodynamic Formalism: A Unified Framework for Kleinian Groups and Non-Archimedean Dynamics,'' declare the following:

\section*{Financial Interests}

\begin{itemize}
\item No author has received any financial compensation, grants, or funding specifically for the preparation of this manuscript that could influence its content.

\item No author has any financial interest (stocks, patents, royalties) related to the subject matter of this paper.

\item No author has received consulting fees, speaker fees, or travel reimbursements from organizations that could benefit from the results of this research.
\end{itemize}

\section*{Non-Financial Interests}

\begin{itemize}
\item No author serves on editorial boards of journals that might compete with the \textit{Annals of Mathematics} for this manuscript.

\item No author has personal relationships with individuals who could be perceived as having influenced this work.

\item No author has intellectual property claims (patents pending or granted) related to the mathematical methods described in this paper.
\end{itemize}
\section*{Institutional Affiliations}

All authors' institutional affiliations are correctly stated in the manuscript. No author has any adjunct or honorary positions at institutions not listed in the affiliation statement.

\section*{Previous Publications}

Some preliminary results from this research program have been posted on arXiv for community feedback:
\begin{itemize}
\item arXiv:2501.xxxxx [math.DS] - ``Preliminary results on fractal spectral asymptotics''
\end{itemize}

These preprints represent early stages of this work and have been substantially revised and expanded for the current submission.

\section*{Concurrent Submissions}

This manuscript is not under consideration at any other journal, and no portion of this work has been submitted elsewhere.

\vspace{3em}

\noindent We confirm that we have no conflicts of interest to declare.

\vspace{3em}

\noindent\rule{7cm}{0.4pt}\\
Date: August 15, 2026

\vspace{2em}

\noindent\rule{7cm}{0.4pt}\\
Signature of Corresponding Author

\end{document}
