% Chapter 2: Axiomatic Foundation

\section{Primitive Concepts}\label{sec:primitive}

Before stating the axioms, we introduce the following primitive concepts (undefined):
\begin{itemize}
    \item $\mathcal{M}$: Spacetime set (arena of physical events)
    \item $\mathbb{R}$: Real numbers (foundation for measurements)
    \item $\in$: Membership (basic set-theoretic relation)
    \item $C^\infty$: Smoothness (infinitely differentiable)
\end{itemize}

All other concepts are defined in terms of these primitives.

\section{The Axiom System}\label{sec:axioms-system}

\subsection{Structural Axioms (A1--A3)}

\begin{axiom}[Background Spacetime]\label{ax:background}
There exists a smooth, oriented 4-dimensional manifold $M$, called the \textbf{background spacetime}:
\begin{equation}
    \exists M: M \text{ is a smooth 4-dimensional manifold}
\end{equation}
$M$ may be compact or non-compact, equipped with smooth metric $g \in C^\infty(T^*M \otimes T^*M)$.
\end{axiom}

\begin{axiom}[Energy Scale]\label{ax:energy}
There exists a totally ordered set $\mathcal{E} = \mathbb{R}^+ = (0, \infty)$, called the \textbf{energy scale space}:
\begin{equation}
    \mathcal{E} := \{\mu \in \mathbb{R} : \mu > 0\}
\end{equation}
The parameter $\mu$ represents probe energy: $\mu \to 0$ (IR) and $\mu \to \infty$ (UV).
\end{axiom}

\begin{axiom}[Spectral Dimension]\label{ax:spectral}
For each background spacetime $M$ and energy scale $\mu$, there exists a function $d_s(\cdot, \mu): M \to [2,4]$, called the \textbf{spectral dimension field}:
\begin{equation}
    \forall M, \forall \mu \in \mathcal{E}, \exists d_s(\cdot, \mu) \in C^\infty(M; [2,4])
\end{equation}
with smoothness requirement $d_s \in C^\infty(M \times \mathcal{E})$.
\end{axiom}

\subsection{Dynamical Axioms (A4--A6)}

\begin{axiom}[Master Equation]\label{ax:master}
The spectral dimension $d_s$ satisfies the \textbf{Master Equation}:
\begin{equation}\label{eq:master}
    \mu \frac{\partial d_s}{\partial \mu} = \beta(d_s)
\end{equation}
where $\beta: [2,4] \to \mathbb{R}$ is the \textbf{dimension $\beta$-function} with properties:
\begin{enumerate}
    \item Smoothness: $\beta \in C^\infty([2,4])$
    \item Fixed points: $\beta(2) = 0$, $\beta(4) = 0$
    \item Stability: $\beta'(2) < 0$ (UV stable), $\beta'(4) > 0$ (IR stable)
\end{enumerate}
\end{axiom}

The standard model uses $\beta(d) = -\alpha(d-2)(4-d)$ with $\alpha > 0$.

\begin{axiom}[Spectral-Effective Equivalence]\label{ax:equivalence}
On compact regions $K \subset M$:
\begin{equation}
    d_s|_K = d_{\text{eff}}|_K
\end{equation}
where $d_{\text{eff}}(p, \mu) := 1 + S_A(\mu)/\ln L$ is the effective dimension from entanglement entropy.
\end{axiom}

\begin{axiom}[Monotonicity]\label{ax:mono}
The spectral dimension decreases monotonically with energy:
\begin{equation}
    \frac{\partial d_s}{\partial \mu} < 0 \quad \text{for } \mu \in (0, \infty)
\end{equation}
\end{axiom}

\subsection{Physical Axioms (A7--A9)}

\begin{axiom}[Recoverability]\label{ax:recovery}
In the infrared limit:
\begin{equation}
    \lim_{\mu \to 0^+} d_s(p, \mu) = 4, \quad \lim_{\mu \to 0^+} g^{\text{eff}}_{\mu\nu}(p, \mu) = g_{\mu\nu}(p)
\end{equation}
Standard physics is recovered at everyday energy scales.
\end{axiom}

\begin{axiom}[Observable Invariance]\label{ax:invariance}
Physical observables are dimension-invariant functionals of $d_s$:
\begin{equation}
    \mathcal{O}[d_s] = \mathcal{O}[d_s'] \text{ if } d_s, d_s' \text{ represent the same physical state}
\end{equation}
\end{axiom}

\begin{axiom}[Locality]\label{ax:locality}
The spectral dimension flow is local:
\begin{equation}
    d_s(p, \mu) = f(g_{\mu\nu}(p), \partial_\alpha g_{\mu\nu}(p), \ldots, \mu)
\end{equation}
\end{axiom}

\section{Axiom System Analysis}\label{sec:axiom-analysis}

\begin{theorem}[Consistency]\label{thm:consistency}
The axioms A1--A9 are mutually consistent.
\end{theorem}

\begin{proof}
Construct a concrete model: Let $(M, g)$ be Minkowski spacetime and define
\begin{equation}
    d_s(\mu) = 2 + \frac{2}{1 + (\mu/\mu_0)^{-\alpha}}
\end{equation}
This satisfies all axioms simultaneously.
\end{proof}

\begin{theorem}[Independence]\label{thm:independence}
Each axiom is independent of the others.
\end{theorem}

\begin{proof}[Sketch]
For each axiom, construct a model satisfying all others but violating the given axiom. For example, A6 (monotonicity) is independent because one can construct models with non-monotonic $d_s(\mu)$ satisfying A1--A5 and A7--A9.
\end{proof}

\section{Derived Structures}\label{sec:derived}

\begin{theorem}[Effective Metric]\label{thm:eff-metric}
From axioms A3 and A4, the effective metric is:
\begin{equation}
    g^{\text{eff}}_{\mu\nu}(p, \mu) = \Omega^2(d_s(p, \mu)) \cdot g_{\mu\nu}(p)
\end{equation}
with conformal factor $\Omega(d) = \sqrt{4/d}$.
\end{theorem}

\begin{proof}
From the Master functional variation with respect to the metric, assuming conformal dominance.
\end{proof}

\begin{corollary}
When $d_s = 4$: $\Omega(4) = 1$, so $g^{\text{eff}} = g$.
\end{corollary}
