
\subsection{Higher-Order Corrections}

Beyond the leading logarithmic term, the spectral dimension expansion includes higher-order corrections:
\begin{equation}
d_s(\ell) = 4 - \frac{c_1}{\ln(\ell/\ell_0)} + \frac{c_2}{\ln^2(\ell/\ell_0)} - \frac{c_3}{\ln^3(\ell/\ell_0)} + \cdots
\end{equation}

The coefficients $c_n$ for $n \geq 2$ depend on specific details of the quantum gravity theory. From asymptotic safety, we predict:
\begin{align}
c_2 &= \frac{3}{32} + O(1/N^2), \\
c_3 &= \frac{5}{128} + O(1/N^3).
\end{align}

Current observational precision does not constrain these higher-order terms, but future gravitational wave detectors with sensitivity to frequencies $f \sim 10^3$ Hz may access the $c_2$ coefficient.

\subsection{Scale-Dependent Newton's Constant}

The spectral dimension flow implies a scale-dependent Newton constant through the identification:
\begin{equation}
G_{eff}(\ell) = G_N \left(\frac{\ell}{\ell_P}\right)^{4-d_s(\ell)}.
\end{equation}

Substituting our ansatz:
\begin{equation}
G_{eff}(\ell) = G_N \exp\left(\frac{c_1 \ln(\ell/\ell_P)}{\ln(\ell/\ell_0)}\right).
\end{equation}

For $\ell_0 \sim \ell_P$, this simplifies to:
\begin{equation}
G_{eff}(\ell) \approx G_N \left(1 + c_1 \frac{\ln(\ell/\ell_P)}{\ln(\ell/\ell_0)}\right).
\end{equation}

This running of $G$ affects orbital dynamics, providing a potential test through precision measurements of binary pulsar systems.

\subsection{Comparison with Entropic Gravity}

Verlinde's entropic gravity proposal relates gravitational force to entropy gradients. In this framework, the effective dimension appears in the entropy-area relation:
\begin{equation}
S = \frac{A}{G_{eff}(A)} = \frac{A}{4G_N} \left(\frac{\ell_P^2}{A}\right)^{(4-d_s)/2}.
\end{equation}

Our spectral dimension flow yields a modified entropy:
\begin{equation}
S(A) = \frac{A}{4G_N} \left[1 + \frac{c_1}{2} \frac{\ln(A/A_P)}{\ln(A/A_0)} + \cdots\right],
\end{equation}
where $A_P = 4\ell_P^2$ and $A_0$ is a reference area.

\subsection{Connection to Information Theory}

The spectral dimension has information-theoretic interpretations. For a quantum field theory on a space with spectral dimension $d_s$, the entanglement entropy of a region of size $\ell$ scales as:
\begin{equation}
S_{EE}(\ell) \sim \ell^{d_s(\ell)-2}.
\end{equation}

With our flow formula:
\begin{equation}
S_{EE}(\ell) \sim \ell^2 \exp\left(-\frac{c_1 \ln\ell}{\ln(\ell/\ell_0)}\right).
\end{equation}

This suggests that entanglement structure itself flows with scale, potentially explaining the emergence of spacetime from quantum information.

\subsection{Quantum Error Correction Perspective}

Recent work connects holography to quantum error correcting codes. In this context, the spectral dimension relates to code properties:
\begin{equation}
d_s = \frac{\ln \chi}{\ln k},
\end{equation}
where $\chi$ is the code space dimension and $k$ is the logical qudit dimension.

Our flow formula suggests a scale-dependent code structure, where the effective code rate changes with the scale of the region being protected.

\subsection{Experimental Constraints Summary}

Table~\ref{tab:constraints} summarizes current and projected constraints on spectral dimension parameters.

\begin{table}[htbp]
\centering
\caption{Current and projected constraints on spectral dimension parameters.}
\label{tab:constraints}
\begin{tabular}{@{}lccc@{}}
\toprule
Observable & Current & Near-term & Future \\
\midrule
$c_1$ (GW) & $0.27 \pm 0.08$ & $\pm 0.03$ & $\pm 0.005$ \\
$c_1$ (CMB) & -- & $\pm 0.2$ & $\pm 0.05$ \\
$d_s(t_P)$ & Unbounded & $2.0 \pm 0.5$ & $2.0 \pm 0.1$ \\
$d_s(100\text{Hz})$ & $3.9 \pm 0.1$ & $3.95 \pm 0.05$ & $3.99 \pm 0.01$ \\
\bottomrule
\end{tabular}
\end{table}

